### 2016-02-04 inputs/results.tex
new figures, updated text to show them

\begin{figure}
\includegraphics[width=0.95\textwidth]{Fig02_Rice-chrom_avg.pdf}
\caption[Rice imputation accuracies]{
imputation accuracies overall, for the major homozygous genotype (AA), and for the minor homozygous genotype (BB) in datasets consisting of 10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\% additional missing values artificially introduced (x-axis) averaged over the 12 rice chromosomes. Lines colors represent the five imputation algorithms: MNI (orange), KNNI (red), SVDI (blue), RFI (green), Beagle with ordered markers (solid black) and Beagle with unordered markers (dashed black).}
\label{fig:accuracy_rice}
\end{figure}

\begin{figure}
\includegraphics[width=0.95\textwidth]{Fig03_Alfalfa_avg.pdf}
\caption[Alfalfa imputation accuracies]{
imputation accuracies overall, for the major homozygous genotype (AA), for heterozygotes (AB), and for the minor homozygous genotype (BB) in datasets consisting of 10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\% additional missing values artificially introduced (x-axis) averaged two alfalfa populations (Alfalfa-Med and Alfalfa-PV). Lines colors represent the five imputation algorithms: MNI (orange), KNNI (red), SVDI (blue), RFI (green) and Beagle (black).}
\label{fig:accuracy_alfalfa}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.95\textwidth]{figure_rice_chrom.pdf}
\caption[Rice imputation accuracies]{
imputation accuracies overall, for the major homozygous genotype (AA), and for the minor homozygous genotype (BB) in datasets consisting of 10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\% additional missing values artificially introduced (x-axis) averaged over the 12 rice chromosomes. Lines colors represent the five imputation algorithms: MNI (orange), KNNI (red), SVDI (blue), RFI (green), Beagle with ordered markers (solid black), Beagle with unordered markers (dashed black), FILLIN with ordered markers (purple) and FILLIN with unordered markers (dashed purple).}
\label{fig:accuracy_rice}
\end{figure}

\begin{figure}
\includegraphics[width=0.95\textwidth]{figure_alfalfa.pdf}
\caption[Alfalfa imputation accuracies]{
imputation accuracies overall, for the major homozygous genotype (AA), for heterozygotes (AB), and for the minor homozygous genotype (BB) in datasets consisting of 10\%, 20\%, 40\% and 70\% allowed missing data per locus (boxes) with 1\%, 5\%, 10\% and 20\% additional missing values artificially introduced (x-axis) averaged two alfalfa populations (Alfalfa-Med and Alfalfa-PV). Lines colors represent the five imputation algorithms: MNI (orange), KNNI (red), SVDI (blue), RFI (green), Beagle with ordered markers (solid black) and Beagle with unordered markers (dashed black). FILLIN was unable to impute alfalfa data and is absent from figure.}
\label{fig:accuracy_alfalfa}
\end{figure}
